Master's Research Proposal

### 2024-05-30 proposal/Proposal.tex
ultimate objective

>>>>

The ultimate objective of this research is to provide a new pathway by which collections of high resolution spatio-temporal movement data that are representative of a species can be used to make a direct impact on fisheries management. It is hoped that this will provide an incentive for creating/enlarging such datasets.
